Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

Since our measurement is fuzzy, generally there are more than one
state consistent with a particular quantum IVPM. For example, consider
three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Then,
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise,}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in question,
and any state is consistent with $\bar{\mu}_{1}$ on any projectors.

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}

\begin{table*}
\caption{\label{table:quantum-interval-expectation}This table highlight the
process to compute $\expval{\mathbf{O}}_{\bar{\mu}_{1}}$. Notice
that $\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$
and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$. }

@@

\end{table*}
Since Eq.~(\ref{eq:quantum-interval-expectation}) is more complex
than Eq.~(\ref{eq:quantum-expectation}), it is instructive to check
an example. Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
and $\mathbf{O}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
By following Table~\ref{table:quantum-interval-expectation}, we
have 
\begin{equation}
\expval{\mathbf{O}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
\end{equation}
$\left[1,2\right]$ is an intuitively result. Since two possible outcomes
are $1$ and $2$, the expectation value is between one of them even
if we no prior knowledge about the likelihood of outcomes. In contrast,
if we naively multiply eigenvalues with intervals, their sum is $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$
which is a worse estimation. Because even if we no prior knowledge,
we know one of them will happen, and estimating the lower-bound by$1\cdot0+2\cdot0=0$
is too pessimistic.

>>>>

Since our measurement is fuzzy, generally there are more than one
state consistent with a particular quantum IVPM. For example, consider
three intervals $\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called \unknown~because
it provides no information. Then,
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a quantum IVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in question,
and any state is consistent with $\bar{\mu}_{1}$ on any projectors.

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express an observable as
its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}

\begin{table*}
\caption{\label{table:quantum-interval-expectation}This table highlights the
process to compute $\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}$. Notice
that $\bar{\mu}_{1}$ is defined by Eq.~(\ref{eq:no-information-IVPM}),
$\mul_{1}$ and $\mur_{1}$ are defined by $\left[\mul_{1}\left(P\right),\mur_{1}\left(P\right)\right]=\bar{\mu}_{1}\left(P\right)$,
and $P_{3}^{+\prime}=\sum_{j\ge3}P_{j}^{s}=\mathbb{0}$. }

@@

\end{table*}
For example, given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Let $J_{\mathrm{z}}=\proj{0}-\proj{2}$,
and $\mathbf{O}_{1}=2\mathbb{1}-J_{\mathrm{z}}^{2}=2\proj{1}+\proj{0}+\proj{2}$.
By following Table~\ref{table:quantum-interval-expectation}, we
have 
\begin{equation}
\expval{\mathbf{O}_{1}}_{\bar{\mu}_{1}}=\sum_{i=1}^{2}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]=\left[1,2\right]\textrm{ .}
\end{equation}
$\left[1,2\right]$ is an intuitively result. Since two possible outcomes
are $1$ and $2$, the expectation value is between one of them even
if we no prior knowledge about the likelihood of outcomes. In contrast,
if we naively multiply eigenvalues with intervals, their sum is $\sum_{i=1}^{2}\lambda_{i}^{+}\bar{\mu}_{1}\left(P_{i}^{+}\right)=\left[0,3\right]$
which is a worse estimation. Because even if we no prior knowledge,
we know one of them will happen, and estimating the lower-bound by$1\cdot0+2\cdot0=0$
is too pessimistic.
